### 2020-06-08 README.Rmd
Miami-Dade FIPS code
Added FIPS 12086 to the example in the paragraph before the r chunk that uses it.

Similar functions are available in the package to create listings of county exposures to storms based on wind, distance to the storm track, and events listings from the NOAA Storm Events Database (flood and tornado events). For example, to get a listing of all storms between 1988 and 2015 for which Miami-Dade county (FIPS: ) has experienced sustained winds of 34 knots or more (17.5 m / s), you can run:

>>>>

Similar functions are available in the package to create listings of county exposures to storms based on wind, distance to the storm track, and events listings from the NOAA Storm Events Database (flood and tornado events). For example, to get a listing of all storms between 1988 and 2015 for which Miami-Dade county (FIPS 12086) has experienced sustained winds of 34 knots or more (17.5 m / s), you can run:
